Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-06-07 paper/results.tex
Removed XMT R-MAT and Triangle results for now. Change Cohen's affiliation.
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@629 3fc257bb-8550-0410-81b3-a5c103da83f7

Also in Figure~\ref{f:rmat}, we compare our MR-MPI implementation with an 
R-MAT generator in MTGL on the Cray XMT.  In the MTGL implementation, 
threads generate edges independently.  A global hash table is used to remove
duplicate edges.  Our MR-MPI implementation runs more quickly than the MTGL
implementation.  The differences in execution time are greatest on 64
processors, where MR-MPI needs the least file I/O for out-of-core operations.

\begin{figure}[htb]
\includegraphics[width=\textwidth]{fig_rmat.pdf}
\caption{Performance of the MR-MPI R-MAT generation algorithm (Figure~\ref{fig:rmat2}) and an MTGL implementation.}
\label{f:rmat}
\end{figure}

@@

In Figure~\ref{f:tri}, we show the performance of the triangle finding 
algorithm (Figure~\ref{fig:tri}).  Execution times for this algorithm were
too large to allow the problem to be run with RMAT-28 on our cluster.
Parallel efficiencies for RMAT-20 ranged from 80\% to 140\%; for RMAT-24, they
ranged from 50\% to 120\%.  Comparisons with an MTGL implementation on the 
Cray XMT give mixed results.  When MR-MPI uses the least file I/O for 
out-of-core operations (e.g., RMAT-20 on 32 and 64 processors), it 
outperforms the MTGL implementation.  However, when significant out-of-core
operations are needed (e.g., for RMAT-24), the MTGL implementation is faster.

\begin{figure}[htb]
\includegraphics[width=\textwidth]{fig_tri.pdf}
\caption{Comparison of triangle-finding implementations using
MR-MPI (Figure~\ref{fig:tri}) and MTGL.}
\label{f:tri}
\end{figure}

>>>>

%Also in Figure~\ref{f:rmat}, we compare our MR-MPI implementation with an 
%R-MAT generator in MTGL on the Cray XMT.  In the MTGL implementation, 
%threads generate edges independently.  A global hash table is used to remove
%duplicate edges.  Our MR-MPI implementation runs more quickly than the MTGL
%implementation.  The differences in execution time are greatest on 64
%processors, where MR-MPI needs the least file I/O for out-of-core operations.

\begin{figure}[htb]
\includegraphics[width=\textwidth]{fig_rmat.pdf}
\caption{Performance of the MR-MPI R-MAT generation algorithm (Figure~\ref{fig:rmat2}) 
%and an MTGL implementation.
}
\label{f:rmat}
\end{figure}

@@

In Figure~\ref{f:tri}, we show the performance of the triangle finding 
algorithm (Figure~\ref{fig:tri}).  Execution times for this algorithm were
too large to allow the problem to be run with RMAT-28 on our cluster.
Parallel efficiencies for RMAT-20 ranged from 80\% to 140\%; for RMAT-24, they
ranged from 50\% to 120\%.  
%Comparisons with an MTGL implementation on the 
%Cray XMT give mixed results.  When MR-MPI uses the least file I/O for 
%out-of-core operations (e.g., RMAT-20 on 32 and 64 processors), it 
%outperforms the MTGL implementation.  However, when significant out-of-core
%operations are needed (e.g., for RMAT-24), the MTGL implementation is faster.

\begin{figure}[htb]
\includegraphics[width=\textwidth]{fig_tri.pdf}
\caption{Performance of the MR-MPI triangle-finding algorithm
(Figure~\ref{fig:tri}).}
\label{f:tri}
\end{figure}

### 2010-06-07 paper/thanks.tex
Removed XMT R-MAT and Triangle results for now. Change Cohen's affiliation.
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@629 3fc257bb-8550-0410-81b3-a5c103da83f7

\section{Acknowledgements}

Sandia is a multiprogram laboratory operated by Sandia Corporation, a
Lockheed Martin Company, for the United States Department of
Energy's National Nuclear Security Administration under contract
DE-AC04-94AL85000.

Hadoop folks.

>>>>

\section{Acknowledgements}
\label{sec:thanks}

We thank the following individuals for their contributions to this
paper: Greg Bayer and Todd Plantenga (Sandia) for explaining Hadoop
concepts to us, and for the Hadoop implementations and timings of
Section~\ref{sec:results}; Jon Cohen (DoD) for fruitful discussions
about his MapReduce graph algorithms~\cite{Cohen09}; Brian Barrett
(Sandia) for the PBGL results of Section~\ref{sec:results}; Jon Berry
(Sandia) for the MTGL results of Section~\ref{sec:results}, and for
his overall support of this work and many useful discussions.

Sandia National Laboratories is a multi-program laboratory operated by
Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
company, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.
